---
title: "Statistical analysis of microclimate and ectotherm outputs"
output: html_document
author: Urban Dajcman
date: "2024-10-3"
fig_width: 9 
fig_height: 7 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message=FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(tidy=TRUE)


```



```{r}
using<-function(...) {
    libs<-unlist(list(...))
    req<-unlist(lapply(libs,require,character.only=TRUE))
    need<-libs[req==FALSE]
    if(length(need)>0){ 
        install.packages(need)
        lapply(need,require,character.only=TRUE)
    }
}
```


```{r}
using("dplyr", "ggplot2", "ggpubr", "rstatix", "NCmisc", "car", "lme4", "DHARMa", "emmeans", "performance", "sjPlot", "rphylopic", "jpeg", "flexplot", "report", "broom", "ggfortify", "MASS", "jtools", "svglite",  "multcomp", "vegan", "showtext", "formatR", "AICcmodavg")
```





```{r}
rm(list = ls())


```



## Prepare modeling data.frames

```{r, warning=FALSE, message=FALSE}
getwd()
load("../../Results/ECTOTHERM_results/results_all_ecto_summerTP.Rda")
res_ecto_stats <- results_all
```


```{r, warning=FALSE, message=FALSE}
#load("../../Results/ECTOTHERM_results/results_all_ecto_springTP.Rda")
#res_ecto_stats_spring <- results_all
```


```{r, warning=FALSE, message=FALSE}
res_ecto_stats$Season <- "SummerTP"
res_ecto_stats_spring$Season <- "SpringTP"

res_ecto_stats
res_ecto_stats_spring


res_both_seasons <- bind_rows(res_ecto_stats, res_ecto_stats_spring)
res_both_seasons

#Get yearly values
res_both_seasons$Forage_year <- res_ecto_stats$Forage/res_ecto_stats$Year 
res_both_seasons$Bask_year <- res_ecto_stats$Bask/res_ecto_stats$Year
res_both_seasons$Fecundity_year <- res_ecto_stats$Fecundity/res_ecto_stats$Year
res_both_seasons

# Calculate average to compare seasons

comparison_df <- res_both_seasons %>%
  group_by(Species, Sintopy, Season) %>%
   summarise(across(c(egg_dev, LifeSpan, Years_repro, Bask_year, Forage_year, Fecundity_year), 
                   list(mean = mean, min = min, max = max), 
                   na.rm = TRUE, 
                   .names = "{col}_{fn}"))

comparison_df

```


```{r, warning=FALSE, message=FALSE}
#Get yearly values
res_ecto_stats$Forage_year <- res_ecto_stats$Forage/res_ecto_stats$Year 
res_ecto_stats$Bask_year <- res_ecto_stats$Bask/res_ecto_stats$Year
res_ecto_stats$Fecundity_year <- res_ecto_stats$Fecundity/res_ecto_stats$Year
res_ecto_stats$Clutches_year <- res_ecto_stats$Clutches/res_ecto_stats$Year

#Rename values
res_ecto_stats$Species[res_ecto_stats$Species == "Ihor"] <- "I. horvathi" 
res_ecto_stats$Species[res_ecto_stats$Species == "Pmur"] <- "P. muralis"

res_ecto_stats$Sintopy[res_ecto_stats$Sintopy == "sint"] <- "Sintopy"
res_ecto_stats$Sintopy[res_ecto_stats$Sintopy == "aloPmur"] <- "Muralis allotopy"
res_ecto_stats$Sintopy[res_ecto_stats$Sintopy == "aloIhor"] <- "Horvathi allotopy"


#Turn to factor
res_ecto_stats$Locality <- as.factor(res_ecto_stats$Locality)
res_ecto_stats$Sintopy <- as.factor(res_ecto_stats$Sintopy)
res_ecto_stats$Species <- as.factor(res_ecto_stats$Species)
str(res_ecto_stats)

res_ecto_stats <- res_ecto_stats %>%
                  rename(Loc_type = Sintopy)


res_ecto_stats <- res_ecto_stats[, c("Locality", "Elevation", "Loc_type", "Species", "MeanTALOC", "MeanRHLOC", "Solar", "NO_Snow", "egg_dev", "LifeSpan", "Years_repro", "Bask_year", "Forage_year", "Fecundity_year")]

head(res_ecto_stats)

str(res_ecto_stats)

## Microclimate analysis table

loc_stats <- res_ecto_stats %>% distinct(MeanTALOC, .keep_all = TRUE)

```

# Models and plots for elevation, species and sintopy analysis

## Mean Temp at location of animal



```{r}
#check data distribution
gghistogram(loc_stats$MeanTALOC, bins = 15)
ggboxplot(loc_stats$MeanTALOC)

#Check lm model
lm_MeanTALOC <- lm(MeanTALOC ~Elevation+Loc_type, data = loc_stats)


# Get summary and p values
summary(lm_MeanTALOC)

    
# Plot

lm_Plot_eTemp <- lm(MeanTALOC ~Elevation, data = loc_stats)

  MeanTemp_plot <- visualize(lm_Plot_eTemp,  MeanTALOC ~Elevation, plot="model")+
                      scale_color_manual(values = c("black"))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean temperature (°C)")), x=NULL)+
    theme(legend.position="null")

    MeanTemp_plot
    
    
#Check model fit, residuals etc.
    
    autoplot(lm_MeanTALOC)+
      theme_classic()
    
    shapiro.test(residuals(lm_MeanTALOC))

  

```


## Mean relative humidity
 
```{r}

#check data distribution
  gghistogram(loc_stats$MeanRHLOC, bins = 15)
  ggboxplot(loc_stats$MeanRHLOC)

#Check lm model first

  lm_MeanRHLOC <- lm(MeanRHLOC ~Elevation+Loc_type, data = loc_stats)


# Get summary and p values
  summary(lm_MeanRHLOC)

# Plot

lm_plot_eHum <- lm(MeanRHLOC ~Elevation, data = loc_stats)
  
  Mean_humid <- visualize(lm_plot_eHum, MeanRHLOC ~ Elevation, plot="model")+
      scale_color_manual(values = c("black"))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean relative humidity (%)")), x=NULL)+
        theme(legend.position="null")
   
  Mean_humid
    
#Check model fit, residuals etc.
    
  autoplot(lm_MeanRHLOC)+
      theme_classic()
  
  shapiro.test(residuals(lm_MeanRHLOC))

  

```
## Mean solar radiation

```{r}
#check data distribution
  gghistogram(loc_stats$Solar, bins = 5)
  ggboxplot(loc_stats$Solar)

#Check lm model first

  lm_Solar <- lm(Solar ~Elevation+Loc_type, data = loc_stats)


# Get summary and p values
  summary(lm_Solar) #AIC delta <4, include interaction
    
# Plot
    
  lm_solar_plot <- lm(Solar ~Elevation, data = loc_stats)
     
  Mean_solar <- visualize(lm_solar_plot,  Solar ~ Elevation, plot="model")+
                         scale_color_manual(values = c("black"))+
      theme_classic()+
      #labs(title = NULL, y="Mean solar radiation (W/m2)", x=NULL)+
    labs(title = NULL, y=expression(paste('Mean solar radiation' ~ " " ~ (W/m^{2}))), x=NULL)+
    labs_pubr()+
    theme(legend.position="null")
  
   Mean_solar
    
    
#Check model fit, residuals etc.
    
    autoplot(lm_Solar)+
      theme_classic()
    
    shapiro.test(residuals(lm_Solar))
    
#Check comparisons
    
    summary(glht(lm_Solar, linfct = mcp(Loc_type = 'Tukey')))

  

```
## Days without snow

```{r}

#check data distribution
gghistogram(loc_stats$NO_Snow, bins = 50)
ggboxplot(loc_stats$NO_Snow)

#Check lm model first

lm_NO_Snow <- lm(NO_Snow ~ Elevation+Loc_type, data = loc_stats)



# Get summary and p values
  summary(lm_NO_Snow)  
    
# Plot
  
  lm_plot_eSnow <- lm(NO_Snow ~ Elevation, data = loc_stats)
  
  SnowDays_plot<- visualize(lm_plot_eSnow, NO_Snow ~ Elevation, plot="model")+
      scale_color_manual(values = c("black"))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Days without snow (n. days)")), x=NULL)+
        theme(legend.position="null")
   SnowDays_plot
    
    
#Check model fit, residuals etc.
    
    autoplot(lm_NO_Snow)+
      theme_classic()
    
    shapiro.test(residuals(lm_NO_Snow))

  

```

## Arrange loc plots

```{r}
plot_micro <- ggarrange(MeanTemp_plot, SnowDays_plot, Mean_solar, Mean_humid, nrow = 2, ncol = 2, labels = NULL,
                       common.legend = TRUE, legend = "none", font.label = list(size=13))

plot_micro


#ggsave("plot_micro_final_udpated.pdf", plot=plot_micro, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
#ggsave("plot_microfinal_updated.svg", plot=plot_micro, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
#ggsave("plot_micro_final_updated.png", plot=plot_micro, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")
```



# Models and plots for elevation, species and sintopy analysis

## Egg development time

```{r}
library(lmerTest)
library(MuMIn)

res_ecto_stats

#check data distribution
gghistogram(res_ecto_stats$egg_dev, bins = 15)+
  theme_pubclean()
ggboxplot(res_ecto_stats$egg_dev)+
  theme_pubclean()+
  labs(y=NULL, x=NULL)

#Check lm model first
lm_eggDev <- lm(egg_dev ~ Elevation+Species+Loc_type, data = res_ecto_stats)
lm_eggDev_int <- lm(egg_dev ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_eggDev_int2<- lm(egg_dev ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_eggDev_int3<- lm(egg_dev ~ Elevation+Loc_type*Species, data = res_ecto_stats)
lm_eggDev_int4<- lm(egg_dev ~ Elevation*Loc_type*Species, data = res_ecto_stats)

lmm_eggDev1 <- lmer(egg_dev ~ Elevation*Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_eggDev2 <- lmer(egg_dev ~ Elevation+Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_eggDev3 <- lmer(egg_dev ~ Elevation*Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_eggDev4 <- lmer(egg_dev ~ Elevation+Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_eggDev5 <- lmer(egg_dev ~ Elevation*Species+Loc_type+(1|Locality), data = res_ecto_stats)


# Compare models using AICc explicitly

# LM
model_list_egg <- list(lm_eggDev, lm_eggDev_int, lm_eggDev_int2, lm_eggDev_int3, lm_eggDev_int4)
model_names_egg <- c("lm_eggDev", "lm_eggDev_int", "lm_eggDev_int2", "lm_eggDev_int3", "lm_eggDev_int4")
aictab(cand.set = model_list_egg, modnames = model_names_egg, second.ord = TRUE)
#LMM

model_list_egg <- list(lmm_eggDev1, lmm_eggDev2, lmm_eggDev3, lmm_eggDev4, lmm_eggDev5)
model_names_egg <- c("lmm_eggDev1", "lmm_eggDev2", "lmm_eggDev3", "lmm_eggDev4", "lmm_eggDev5")
aictab(cand.set = model_list_egg, modnames = model_names_egg, second.ord = TRUE)

summary(lm_eggDev) ## NO SIGNIFICANT INTERACTIONS
summary(lmm_eggDev2) ## NO SIGNIFICANT INTERACTIONS

Anova(lm_eggDev, type = 2)

# Get summary and p values

    visualize(lm_eggDev)
    
   EggDev_plot <- visualize(lm_eggDev, egg_dev~Elevation+Loc_type |Species, method="lm", plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
     scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Egg development time (days)")), x=NULL)+
      theme(
        strip.text = element_text(face = "italic"),
        axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
   
   EggDev_plot
   
ggsave("plot_ecto_eggdev.pdf", plot=EggDev_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_eggdev.svg", plot=EggDev_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_eggdev.png", plot=EggDev_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")
    

   
#Check model fit, residuals etc.
    
    autoplot(lm_eggDev)+
      theme_classic()
    
    shapiro.test(residuals(lm_eggDev))
    
    
#Check comparisons
    summary(glht(lm_eggDev, linfct = mcp(Loc_type = 'Tukey')))
    

    
```


## Lifespan

```{r}

#check data
gghistogram(res_ecto_stats$LifeSpan, bins = 6)
ggboxplot(res_ecto_stats$LifeSpan)

#Check lm model first

lm_Lifespan <- lm(LifeSpan ~ Elevation + Species+ Loc_type, data = res_ecto_stats)
lm_Lifespan_int <- lm(LifeSpan ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_Lifespan_int2<- lm(LifeSpan ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_Lifespan_int3<- lm(LifeSpan ~ Elevation+Loc_type*Species, data = res_ecto_stats)
lm_Lifespan_int4<- lm(LifeSpan ~ Elevation*Loc_type*Species, data = res_ecto_stats)


lmm_Lifespan1 <- lmer(LifeSpan ~ Elevation*Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_Lifespan2 <- lmer(LifeSpan ~ Elevation+Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_Lifespan3 <- lmer(LifeSpan ~ Elevation*Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_Lifespan4 <- lmer(LifeSpan ~ Elevation+Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_Lifespan5 <- lmer(LifeSpan ~ Elevation*Species+Loc_type+(1|Locality), data = res_ecto_stats)


# Compare models using AICc explicitly

# LM
model_list_lifespan <- list(lm_Lifespan, lm_Lifespan_int, lm_Lifespan_int2, lm_Lifespan_int3, lm_Lifespan_int4)
model_names_lifespan <- c("lm_Lifespan", "lm_Lifespan_int", "lm_Lifespan_int2", "lm_Lifespan_int3", "lm_Lifespan_int4")
aictab(cand.set = model_list_lifespan, modnames = model_names_lifespan, second.ord = TRUE)

# LMM
model_list_lifespanLMM <- list(lmm_Lifespan1, lmm_Lifespan2, lmm_Lifespan3, lmm_Lifespan4, lmm_Lifespan5)
model_names_lifespanLMM <- c("lmm_Lifespan1", "lmm_Lifespan2", "lmm_Lifespan3", "lmm_Lifespan4", "lmm_Lifespan5")
aictab(cand.set = model_list_lifespanLMM, modnames = model_names_lifespanLMM, second.ord = TRUE)


summary(lm_Lifespan) ## NO SIGNIFICANT INTERACTIONS, CHECKED MODELS BY AIC AND COMPARED FITS
Anova(lm_Lifespan, type = 2)

summary(lmm_Lifespan2)



# Get summary and p values

     visualize(lm_Lifespan)
    
    Lifespan_plot <-   visualize(lm_Lifespan, LifeSpan~Elevation + Loc_type|Species, method="lm", plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
      scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Lifespan (years)")), x=NULL)+
      theme(
        #strip.text = element_text(face = "italic"),
         #axis.text=element_text(size=11),
        #axis.title=element_text(size=12,face="bold")
        strip.background = element_blank(),
  strip.text.x = element_blank())+
    facet_wrap(~Species)
  Lifespan_plot
  
              ggsave("plot_ecto_lifespan.pdf", plot=Lifespan_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_lifespan.svg", plot=Lifespan_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_lifespan.png", plot=Lifespan_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")
  
    
    
    #Check model fit, residuals etc.
    
    autoplot(lm_Lifespan)+
      theme_classic()
    
    shapiro.test(residuals(lm_Lifespan))
    
   #Check comparisons
    
    summary(glht(lm_Lifespan, linfct = mcp(Loc_type = 'Tukey')))
    

```

## Years reproducing

```{r}

#check data
gghistogram(res_ecto_stats$Years_repro, bins = 8)
ggboxplot(res_ecto_stats$Years_repro)


#Check lm model first
lm_YearsRepro_noLoc <- lm(Years_repro ~ Elevation + Species, data = res_ecto_stats)
lm_YearsRepro <- lm(Years_repro ~ Elevation + Species + Loc_type, data = res_ecto_stats)
lm_YearsRepro_int <- lm(Years_repro ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_YearsRepro_int2<- lm(Years_repro ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_YearsRepro_int3<- lm(Years_repro ~ Elevation+Loc_type*Species, data = res_ecto_stats)
lm_YearsRepro_int4<- lm(Years_repro ~ Elevation*Loc_type*Species, data = res_ecto_stats)


lmm_yearsRepro1 <- lmer(Years_repro ~ Elevation*Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_yearsRepro2 <- lmer(Years_repro ~ Elevation+Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_yearsRepro3 <- lmer(Years_repro ~ Elevation*Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_yearsRepro4 <- lmer(Years_repro ~ Elevation+Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_yearsRepro5 <- lmer(Years_repro ~ Elevation*Species+Loc_type+(1|Locality), data = res_ecto_stats)


# Compare models using AICc explicitly

# LM
model_list_years <- list(lm_YearsRepro_noLoc, lm_YearsRepro, lm_YearsRepro_int, lm_YearsRepro_int2,   lm_YearsRepro_int3, lm_YearsRepro_int4)
model_names_years <- c("lm_YearsRepro_noLoc", "lm_YearsRepro", "lm_YearsRepro_int", "lm_YearsRepro_int2",   "lm_YearsRepro_int3", "lm_YearsRepro_int4")

aictab(cand.set = model_list_years, modnames = model_names_years, second.ord = TRUE)

# LMM
model_list_yearsLMM <- list(lmm_yearsRepro1, lmm_yearsRepro2, lmm_yearsRepro3, lmm_yearsRepro4, lmm_yearsRepro5)
model_names_yearsLMM <- c("lmm_yearsRepro1", "lmm_yearsRepro2", "lmm_yearsRepro3", "lmm_yearsRepro4", "lmm_yearsRepro5")
aictab(cand.set = model_list_yearsLMM, modnames = model_names_yearsLMM, second.ord = TRUE)


summary(lm_YearsRepro_noLoc) ## OPT FOR SIMPLER MODEL
Anova(lm_YearsRepro_noLoc)

summary(lmm_yearsRepro2)



# Get summary and p values
  
    
  visualize(lm_YearsRepro_noLoc)
    
  YearsRepro_plot <-  visualize(lm_YearsRepro_noLoc, Years_repro~Elevation | Species, method="lm", plot="model")+
                scale_color_manual(values = c("black"))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Years reproducing (years)")), x=NULL)+
        theme(strip.background = element_blank(),
  strip.text.x = element_blank(),
  axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
  
  YearsRepro_plot
  
            ggsave("plot_ecto_yrepro.pdf", plot=YearsRepro_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_yrepro.svg", plot=YearsRepro_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_yrepro.png", plot=YearsRepro_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")
    
    
    #Check model fit, residuals etc.
    
    autoplot(lm_YearsRepro_noLoc)+
      theme_classic()
    
    shapiro.test(residuals(lm_YearsRepro_noLoc))
    
  
```


## Yearly basking time FROM HERE ON ADD LMM

```{r}

#check data
gghistogram(res_ecto_stats$Bask_year, bins = 8)
ggboxplot(res_ecto_stats$Bask_year)


#Check lm model first
lm_BaskYear <- lm(Bask_year ~ Elevation + Species + Loc_type, data = res_ecto_stats)
lm_BaskYear_int <- lm(Bask_year ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_BaskYear_int2<- lm(Bask_year ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_BaskYear_int3<- lm(Bask_year ~ Elevation+Loc_type*Species, data = res_ecto_stats)
lm_BaskYear_int4<- lm(Bask_year ~ Elevation*Loc_type*Species, data = res_ecto_stats)

lmm_BaskYear1 <- lmer(Bask_year ~ Elevation*Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_BaskYear2 <- lmer(Bask_year ~ Elevation+Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_BaskYear3 <- lmer(Bask_year ~ Elevation*Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_BaskYear4 <- lmer(Bask_year ~ Elevation+Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_BaskYear5 <- lmer(Bask_year ~ Elevation*Species+Loc_type+(1|Locality), data = res_ecto_stats)


# Compare models using AICc explicitly

# LM
model_list_Bask <- list(lm_BaskYear, lm_BaskYear_int, lm_BaskYear_int2, lm_BaskYear_int3,   lm_BaskYear_int4)
model_names_Bask <- c("lm_BaskYear", "lm_BaskYear_int", "lm_BaskYear_int2", "lm_BaskYear_int3",   "lm_BaskYear_int4")
aictab(cand.set = model_list_Bask, modnames = model_names_Bask, second.ord = TRUE)


# LMM
model_list_BaskLMM <- list(lmm_BaskYear1, lmm_BaskYear2, lmm_BaskYear3, lmm_BaskYear4, lmm_BaskYear5)
model_names_BaskLMM <- c("lmm_BaskYear1", "lmm_BaskYear2", "lmm_BaskYear3", "lmm_BaskYear4", "lmm_BaskYear5")
aictab(cand.set = model_list_BaskLMM, modnames = model_names_BaskLMM, second.ord = TRUE)


summary(lm_BaskYear) ## NO SIGNIFICANT INTERACTIONS
Anova(lm_BaskYear)

summary(lmm_BaskYear4)



# Get summary and p values

    visualize(lm_BaskYear)
    
    Basking_plot <- visualize(lm_BaskYear, Bask_year~Elevation + Loc_type|Species, method="lm", plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
      scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean yearly basking time (hours)")), x=NULL)+
          theme(strip.background = element_blank(),
  strip.text.x = element_blank(),
   axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
    
    Basking_plot
    
          ggsave("plot_ecto_baske.pdf", plot=Basking_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_baske.svg", plot=Basking_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_baske.png", plot=Basking_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")

    #Check model fit, residuals etc.
    
    autoplot(lm_BaskYear)+
      theme_classic()
    
    shapiro.test(residuals(lm_BaskYear))
    
   #Check comparisons
            
    summary(glht(lm_BaskYear, linfct = mcp(Loc_type = 'Tukey')))
 

```

## Forage time



```{r}

#check data
gghistogram(res_ecto_stats$Forage_year, bins = 8)
ggboxplot(res_ecto_stats$Forage_year)


#Check lm model first

lm_ForageYear <- lm(Forage_year ~ Elevation + Species + Loc_type, data = res_ecto_stats)
lm_ForageYear_int <- lm(Forage_year ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_ForageYear_int2<- lm(Forage_year ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_ForageYear_int3<- lm(Forage_year ~ Elevation+Loc_type*Species, data = res_ecto_stats)
lm_ForageYear_int4<- lm(Forage_year ~ Elevation*Loc_type*Species, data = res_ecto_stats)

lmm_ForageYear1 <- lmer(Forage_year ~ Elevation*Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_ForageYear2 <- lmer(Forage_year ~ Elevation+Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_ForageYear3 <- lmer(Forage_year ~ Elevation*Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_ForageYear4 <- lmer(Forage_year ~ Elevation+Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_ForageYear5 <- lmer(Forage_year ~ Elevation*Species+Loc_type+(1|Locality), data = res_ecto_stats)


# Compare models using AICc explicitly
# LM
model_list_Forage <- list(lm_ForageYear, lm_ForageYear_int, lm_ForageYear_int2, lm_ForageYear_int3, lm_ForageYear_int4)
model_names_Forage <- c("lm_ForageYear", "lm_ForageYear_int", "lm_ForageYear_int2", "lm_ForageYear_int3", "lm_ForageYear_int4")
aictab(cand.set = model_list_Forage, modnames = model_names_Forage, second.ord = TRUE)

# LMM
model_list_ForageLMM <- list(lmm_ForageYear1, lmm_ForageYear2, lmm_ForageYear3, lmm_ForageYear4, lmm_ForageYear5)
model_names_ForageLMM <- c("lmm_ForageYear1", "lmm_ForageYear2", "lmm_ForageYear3", "lmm_ForageYear4", "lmm_ForageYear5")
aictab(cand.set = model_list_ForageLMM, modnames = model_names_ForageLMM, second.ord = TRUE)




summary(lm_ForageYear) ## NO SIGNIFICANT INTERACTION -> use this one
Anova(lm_ForageYear, type = 2)

summary(lm_ForageYear_int) ## delta AICc o.27 interaction elev*species
Anova(lm_ForageYear_int, type=3)

summary(lmm_ForageYear4)

    
# Plot
    
    visualize(lm_ForageYear)
   
    Forage_plot <-  visualize(lm_ForageYear, Forage_year~Elevation + Loc_type|Species,method="lm", plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
                scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean yearly foraging time (hours)")), x="Elevation (m)")+
          theme(strip.background = element_blank(),
  strip.text.x = element_blank(),
   axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
    
    Forage_plot
    
      ggsave("plot_ecto_forage.pdf", plot=Forage_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_forage.svg", plot=Forage_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_forage.png", plot=Forage_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")
    
    
    #Check model fit, residuals etc.
    
    autoplot(lm_ForageYear)+
      theme_classic()
    
    shapiro.test(residuals(lm_ForageYear))

    
   #Check comparisons
    
    summary(glht(lm_ForageYear, linfct = mcp(Loc_type = 'Tukey')))
 


```


## Fecundity per year

```{r}

#check data distribution
gghistogram(res_ecto_stats$Fecundity_year, bins = 15)
ggboxplot(res_ecto_stats$Fecundity_year)

#Check lm model first

lm_FecundityYear <- lm(Fecundity_year ~Elevation+Species+Loc_type, data = res_ecto_stats)
lm_FecundityYear_int <- lm(Fecundity_year ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_FecundityYear_int2<- lm(Fecundity_year ~Elevation*Loc_type+Species, data = res_ecto_stats)
lm_FecundityYear_int3<- lm(Fecundity_year ~Elevation+Loc_type*Species, data = res_ecto_stats)
lm_FecundityYear_int4<- lm(Fecundity_year ~Elevation*Loc_type*Species, data = res_ecto_stats)

lmm_FecundityYear1 <- lmer(Fecundity_year ~ Elevation*Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_FecundityYear2 <- lmer(Fecundity_year ~ Elevation+Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_FecundityYear3 <- lmer(Fecundity_year ~ Elevation*Loc_type+Species+(1|Locality), data = res_ecto_stats)
lmm_FecundityYear4 <- lmer(Fecundity_year ~ Elevation+Loc_type*Species+(1|Locality), data = res_ecto_stats)
lmm_FecundityYear5 <- lmer(Fecundity_year ~ Elevation*Species+Loc_type+(1|Locality), data = res_ecto_stats)


# Compare models using AICc explicitly

# LM
model_list_Fecundity <- list(lm_FecundityYear, lm_FecundityYear_int, lm_FecundityYear_int2, lm_FecundityYear_int3, lm_FecundityYear_int4)
model_names_Fecundity <- c("lm_FecundityYear", "lm_FecundityYear_int", "lm_FecundityYear_int2", "lm_FecundityYear_int3", "lm_FecundityYear_int4")
aictab(cand.set = model_list_Fecundity, modnames = model_names_Fecundity, second.ord = TRUE)

# LMM
model_list_FecundityLMM <- list(lmm_FecundityYear1, lmm_FecundityYear2, lmm_FecundityYear3, lmm_FecundityYear4, lmm_FecundityYear5)
model_names_FecundityLMM <- c("lmm_FecundityYear1", "lmm_FecundityYear2", "lmm_FecundityYear3", "lmm_FecundityYear4", "lmm_FecundityYear5")
aictab(cand.set = model_list_ForageLMM, modnames = model_names_ForageLMM, second.ord = TRUE)


summary(lm_FecundityYear_int) ##  interaction between elevation and species
Anova(lm_FecundityYear_int, type = 3)




    
  # Plot
    visualize(lm_FecundityYear_int)
    
  Fecundity_plot <-  visualize(lm_FecundityYear_int, Fecundity_year~Elevation + Loc_type|Species, method="lm", plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
                scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
     theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean yearly fecundity \n      (n. offspring)")), x="Elevation (m)")+
    theme(strip.background = element_blank(),
  strip.text.x = element_blank(),
  axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
  

  
  Fecundity_plot
  

  ggsave("plot_ecto_fecundity.pdf", plot=Fecundity_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_fecundity.svg", plot=Fecundity_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_fecundity.png", plot=Fecundity_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")
  
    
    
#Check model fit, residuals etc.
    
    autoplot(lm_FecundityYear_int)+
      theme_classic()
    
    shapiro.test(residuals(lm_FecundityYear_int))
    
#Check comparisons
    summary(glht(lm_FecundityYear_int, linfct = mcp(Loc_type = 'Tukey')))
    
  
```




## Arrange plots

```{r}
plot_ecto <- ggarrange(EggDev_plot, Lifespan_plot, YearsRepro_plot, Basking_plot, Forage_plot, Fecundity_plot, nrow = 3, ncol = 2, labels = NULL, common.legend = FALSE, legend = "none", font.label = list(size = 13, color = "black", face = "bold"))

plot_ecto


ggsave("plot_ecto_final_updated.pdf", plot=plot_ecto, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_final_updated.svg", plot=plot_ecto, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_final_updated.png", plot=plot_ecto, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")

plot_ecto_vert <- ggarrange(EggDev_plot, Lifespan_plot, YearsRepro_plot, Basking_plot, Forage_plot, Fecundity_plot, nrow = 6, ncol = 1, labels = NULL, common.legend = FALSE, legend = "none", font.label = list(size = 13, color = "black", face = "bold"))

plot_ecto_vert


ggsave("plot_ecto_vert.pdf", plot=plot_ecto_vert, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=35, dpi=300)
ggsave("plot_ecto_vert.svg", plot=plot_ecto_vert, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=35, dpi=300)
ggsave("plot_ecto_vert.png", plot=plot_ecto_vert, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=35, dpi=300, bg="white")
```



## Elevation plot

```{r}

loc_colors = c("Horvathi allotopy"="firebrick", "Muralis allotopy"="gold", "Sintopy"="navyblue")

elev_plot_data <- res_ecto_stats %>% dplyr::select("Locality", "Elevation", "Loc_type") %>% distinct()

elev_plot_data




elevations_descriptive_plot <-ggplot(elev_plot_data, aes(x = Elevation, y = Elevation, color=Loc_type)) +
  geom_jitter(size=14, width = 50, height=0) +
  scale_color_manual(values = loc_colors) +  
  labs(y = "Elevation (m)") +
  theme_classic()+
  theme(axis.title.x = element_blank(),        
        axis.text.x = element_blank(),          
        axis.ticks.x = element_blank(),
         axis.line.x = element_blank(),          
        legend.position = "none",
        axis.title.y = element_text(size = 34),
        axis.text.y = element_text(size = 30))  

elevations_descriptive_plot


ggsave("elevations_descriptive_plot.pdf", plot=elevations_descriptive_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=15, height=20, dpi=300)
ggsave("elevations_descriptive_plot.svg", plot=elevations_descriptive_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=15, height=20, dpi=300)
ggsave("elevations_descriptive_plot.png", plot=elevations_descriptive_plot, path = "../../Figures/Ectotherm_plots/", units="cm", width=15, height=20, dpi=300, bg="white")
```


## Summary tables for supplementary material

### LM results

```{r}
summary(lm_eggDev)
summary(lm_Lifespan)
summary(lm_YearsRepro_noLoc)
summary(lm_BaskYear)
summary(lm_ForageYear) 
summary(lm_FecundityYear_int)

```


### Post-hoc comparison

```{r}
 summary(glht(lm_eggDev, linfct = mcp(Loc_type = 'Tukey')))
 summary(glht(lm_Lifespan, linfct = mcp(Loc_type = 'Tukey')))
 summary(glht(lm_BaskYear, linfct = mcp(Loc_type = 'Tukey')))
 summary(glht(lm_ForageYear, linfct = mcp(Loc_type = 'Tukey')))
 summary(glht(lm_FecundityYear_int, linfct = mcp(Loc_type = 'Tukey')))
```


