---
title: "Statistical analysis of microclimate and ectotherm outputs"
output: html_document
author: Urban Dajcman
date: "2023-10-26"
fig_width: 9 
fig_height: 7 

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message=FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(tidy=TRUE)


```



```{r}


using<-function(...) {
    libs<-unlist(list(...))
    req<-unlist(lapply(libs,require,character.only=TRUE))
    need<-libs[req==FALSE]
    if(length(need)>0){ 
        install.packages(need)
        lapply(need,require,character.only=TRUE)
    }
}


using("dplyr", "ggplot2", "ggpubr", "rstatix", "NCmisc", "car", "lme4", "DHARMa", "emmeans", "performance", "sjPlot", "rphylopic", "jpeg", "flexplot", "report", "broom", "ggfortify", "MASS", "jtools", "svglite",  "multcomp", "vegan", "showtext", "formatR")

rm(list = ls())

```



## Prepare modeling data.frames

```{r, warning=FALSE, message=FALSE}
getwd()
load("../../Results/ECTOTHERM_results/results_all_ecto2.Rda")
res_ecto_stats <- results_all

#Get yearly values
res_ecto_stats$Forage_year <- res_ecto_stats$Forage/res_ecto_stats$Year 
res_ecto_stats$Bask_year <- res_ecto_stats$Bask/res_ecto_stats$Year
res_ecto_stats$Fecundity_year <- res_ecto_stats$Fecundity/res_ecto_stats$Year
res_ecto_stats$Clutches_year <- res_ecto_stats$Clutches/res_ecto_stats$Year

#Rename values
res_ecto_stats$Species[res_ecto_stats$Species == "Ihor"] <- "I. horvathi" 
res_ecto_stats$Species[res_ecto_stats$Species == "Pmur"] <- "P. muralis"

res_ecto_stats$Sintopy[res_ecto_stats$Sintopy == "sint"] <- "Sintopy"
res_ecto_stats$Sintopy[res_ecto_stats$Sintopy == "aloPmur"] <- "Muralis allotopy"
res_ecto_stats$Sintopy[res_ecto_stats$Sintopy == "aloIhor"] <- "Horvathi allotopy"


#Turn to factor
res_ecto_stats$Locality <- as.factor(res_ecto_stats$Locality)
res_ecto_stats$Sintopy <- as.factor(res_ecto_stats$Sintopy)
res_ecto_stats$Species <- as.factor(res_ecto_stats$Species)
str(res_ecto_stats)

res_ecto_stats <- res_ecto_stats %>%
                  rename(Loc_type = Sintopy)


res_ecto_stats <- res_ecto_stats[, c( "Elevation", "Loc_type", "Species", "MeanTALOC", "MeanRHLOC", "Solar", "NO_Snow", "egg_dev", "LifeSpan",
                                      "Years_repro", "Bask_year", "Forage_year", "Fecundity_year")]

head(res_ecto_stats)

str(res_ecto_stats)

## Microclimate analysis table

loc_stats <- res_ecto_stats %>% distinct(MeanTALOC, .keep_all = TRUE)

```

# Models and plots for elevation, species and sintopy analysis

## Mean Temp at location of animal



```{r}
#check data distribution
gghistogram(loc_stats$MeanTALOC, bins = 15)
ggboxplot(loc_stats$MeanTALOC)

#Check lm model
lm_MeanTALOC <- lm(MeanTALOC ~Elevation+Loc_type, data = loc_stats)


# Get summary and p values
summary(lm_MeanTALOC)

    
# Plot

lm_Plot_eTemp <- lm(MeanTALOC ~Elevation, data = loc_stats)

  MeanTemp_plot <- visualize(lm_Plot_eTemp,  MeanTALOC ~Elevation, plot="model")+
                      scale_color_manual(values = c("black"))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean temperature (°C)")), x=NULL)+
    theme(legend.position="null")

    MeanTemp_plot
    
    
#Check model fit, residuals etc.
    
    autoplot(lm_MeanTALOC)+
      theme_classic()
    
    shapiro.test(residuals(lm_MeanTALOC))

  

```


## Mean relative humidity
 
```{r}

#check data distribution
  gghistogram(loc_stats$MeanRHLOC, bins = 15)
  ggboxplot(loc_stats$MeanRHLOC)

#Check lm model first

  lm_MeanRHLOC <- lm(MeanRHLOC ~Elevation+Loc_type, data = loc_stats)


# Get summary and p values
  summary(lm_MeanRHLOC)

# Plot

lm_plot_eHum <- lm(MeanRHLOC ~Elevation, data = loc_stats)
  
  Mean_humid <- visualize(lm_plot_eHum, MeanRHLOC ~ Elevation, plot="model")+
      scale_color_manual(values = c("black"))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean relative humidity (%)")), x=NULL)+
        theme(legend.position="null")
   
  Mean_humid
    
#Check model fit, residuals etc.
    
  autoplot(lm_MeanRHLOC)+
      theme_classic()
  
  shapiro.test(residuals(lm_MeanRHLOC))

  

```
## Mean solar radiation

```{r}
#check data distribution
  gghistogram(loc_stats$Solar, bins = 5)
  ggboxplot(loc_stats$Solar)

#Check lm model first

  lm_Solar <- lm(Solar ~Elevation+Loc_type, data = loc_stats)


# Get summary and p values
  summary(lm_Solar) #AIC delta <4, include interaction
    
# Plot
    
  lm_solar_plot <- lm(Solar ~Elevation, data = loc_stats)
     
  Mean_solar <- visualize(lm_solar_plot,  Solar ~ Elevation, plot="model")+
                         scale_color_manual(values = c("black"))+
      theme_classic()+
      #labs(title = NULL, y="Mean solar radiation (W/m2)", x=NULL)+
    labs(title = NULL, y=expression(paste('Mean solar radiation' ~ " " ~ (W/m^{2}))), x=NULL)+
    labs_pubr()+
    theme(legend.position="null")
  
   Mean_solar
    
    
#Check model fit, residuals etc.
    
    autoplot(lm_Solar)+
      theme_classic()
    
    shapiro.test(residuals(lm_Solar))
    
#Check comparisons
    
    summary(glht(lm_Solar, linfct = mcp(Loc_type = 'Tukey')))

  

```
## Days without snow

```{r}

#check data distribution
gghistogram(loc_stats$NO_Snow, bins = 50)
ggboxplot(loc_stats$NO_Snow)

#Check lm model first

lm_NO_Snow <- lm(NO_Snow ~ Elevation+Loc_type, data = loc_stats)



# Get summary and p values
  summary(lm_NO_Snow)  
    
# Plot
  
  lm_plot_eSnow <- lm(NO_Snow ~ Elevation, data = loc_stats)
  
  SnowDays_plot<- visualize(lm_plot_eSnow, NO_Snow ~ Elevation, plot="model")+
      scale_color_manual(values = c("black"))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Days without snow (n. days)")), x=NULL)+
        theme(legend.position="null")
   SnowDays_plot
    
    
#Check model fit, residuals etc.
    
    autoplot(lm_NO_Snow)+
      theme_classic()
    
    shapiro.test(residuals(lm_NO_Snow))

  

```

## Arrange loc plots

```{r}
plot_micro <- ggarrange(MeanTemp_plot, SnowDays_plot, Mean_solar, Mean_humid, nrow = 2, ncol = 2, labels = NULL,
                       common.legend = TRUE, legend = "none", font.label = list(size=13))

plot_micro


ggsave("plot_micro_final.pdf", plot=plot_micro, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_microfinal.svg", plot=plot_micro, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_micro_final.png", plot=plot_micro, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")
```



# Models and plots for elevation, species and sintopy analysis

## Egg development time

```{r}
#check data distribution
gghistogram(res_ecto_stats$egg_dev, bins = 15)+
  theme_pubclean()
ggboxplot(res_ecto_stats$egg_dev)+
  theme_pubclean()+
  labs(y=NULL, x=NULL)

#Check lm model first
lm_eggDev <- lm(egg_dev ~ Elevation+Species+Loc_type, data = res_ecto_stats)
lm_eggDev_int <- lm(egg_dev ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_eggDev_int2<- lm(egg_dev ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_eggDev_int3<- lm(egg_dev ~ Elevation+Loc_type*Species, data = res_ecto_stats)


compare.fits(egg_dev ~Elevation | Species+
               Loc_type, data = res_ecto_stats, lm_eggDev, lm_eggDev_int)

compare.fits(egg_dev ~Elevation | Species+
               Loc_type, data = res_ecto_stats, lm_eggDev, lm_eggDev_int2)

compare.fits(egg_dev ~Elevation | Species+
               Loc_type, data = res_ecto_stats, lm_eggDev, lm_eggDev_int3)


AIC(lm_eggDev, lm_eggDev_int, lm_eggDev_int2, lm_eggDev_int3)
anova(lm_eggDev, lm_eggDev_int, lm_eggDev_int2, lm_eggDev_int3)

summary(lm_eggDev) ## NO SIGNIFICANT INTERACTIONS

#summary(lm_eggDev_int)
#summary(lm_eggDev_int2)
#summary(lm_eggDev_int3)

# Get summary and p values

    visualize(lm_eggDev)
    
   EggDev_plot <- visualize(lm_eggDev, egg_dev~Elevation+Loc_type |Species, plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
     scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Egg development time (days)")), x=NULL)+
      theme(
        strip.text = element_text(face = "italic"),
        axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
   
   EggDev_plot
    

   
#Check model fit, residuals etc.
    
    autoplot(lm_eggDev)+
      theme_classic()
    
    shapiro.test(residuals(lm_eggDev))
    
#Check comparisons
    summary(glht(lm_eggDev, linfct = mcp(Loc_type = 'Tukey')))
    

    
```


## Lifespan

```{r}

#check data
gghistogram(res_ecto_stats$LifeSpan, bins = 4)
ggboxplot(res_ecto_stats$LifeSpan)

#Check lm model first



lm_Lifespan <- lm(LifeSpan ~ Elevation + Species+ Loc_type, data = res_ecto_stats)
lm_Lifespan_int <- lm(LifeSpan ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_Lifespan_int2<- lm(LifeSpan ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_Lifespan_int3<- lm(LifeSpan ~ Elevation+Loc_type*Species, data = res_ecto_stats)


compare.fits(LifeSpan ~Elevation | Species+Loc_type,
             data = res_ecto_stats, lm_Lifespan, lm_Lifespan_int)

compare.fits(LifeSpan ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_Lifespan, lm_Lifespan_int2)

compare.fits(LifeSpan ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_Lifespan, lm_Lifespan_int3)


AIC(lm_Lifespan, lm_Lifespan_int, lm_Lifespan_int2, lm_Lifespan_int3)

anova(lm_Lifespan, lm_Lifespan_int, lm_Lifespan_int2, lm_Lifespan_int3)

summary(lm_Lifespan) ## NO SIGNIFICANT INTERACTIONS, CHECKED MODELS BY AIC AND COMPARED FITS
#summary(lm_Lifespan_int)
#summary(lm_Lifespan_int2)
#summary(lm_Lifespan_int3)



# Get summary and p values

     visualize(lm_Lifespan_int2)
    
    Lifespan_plot <-   visualize(lm_Lifespan, LifeSpan~Elevation + Loc_type|Species, plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
      scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Lifespan (years)")), x=NULL)+
      theme(
        strip.text = element_text(face = "italic"),
         axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
  Lifespan_plot
  
    
    
    #Check model fit, residuals etc.
    
    autoplot(lm_Lifespan_int2)+
      theme_classic()
    
    shapiro.test(residuals(lm_Lifespan_int2))
    
   #Check comparisons
    
    summary(glht(lm_Lifespan, linfct = mcp(Loc_type = 'Tukey')))
    

```

## Years reproducing

```{r}

#check data
gghistogram(res_ecto_stats$Years_repro, bins = 8)
ggboxplot(res_ecto_stats$Years_repro)


#Check lm model first
lm_YearsRepro_noLoc <- lm(Years_repro ~ Elevation + Species, data = res_ecto_stats)
lm_YearsRepro <- lm(Years_repro ~ Elevation + Species + Loc_type, data = res_ecto_stats)
lm_YearsRepro_int <- lm(Years_repro ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_YearsRepro_int2<- lm(Years_repro ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_YearsRepro_int3<- lm(Years_repro ~ Elevation+Loc_type*Species, data = res_ecto_stats)



compare.fits(Years_repro ~Elevation | Species+Loc_type,
             data = res_ecto_stats, lm_YearsRepro, lm_YearsRepro_int)

compare.fits(Years_repro ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_YearsRepro, lm_YearsRepro_int2)

compare.fits(Years_repro ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_YearsRepro, lm_YearsRepro_int3)


AIC(lm_YearsRepro, lm_YearsRepro_int, lm_YearsRepro_int2, lm_YearsRepro_int3, lm_YearsRepro_noLoc)
anova(lm_YearsRepro_noLoc, lm_YearsRepro, lm_YearsRepro_int, lm_YearsRepro_int2, lm_YearsRepro_int3)

summary(lm_YearsRepro_noLoc) ## OPT FOR SIMPLER MODEL

#summary(lm_YearsRepro_int)
#summary(lm_YearsRepro_int2) 
#summary(lm_YearsRepro_int3)


# Get summary and p values
  
    
  visualize(lm_YearsRepro_noLoc)
    
  YearsRepro_plot <-  visualize(lm_YearsRepro_noLoc, Years_repro~Elevation | Species, plot="model")+
                scale_color_manual(values = c("black"))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Years reproducing (years)")), x=NULL)+
        theme(strip.background = element_blank(),
  strip.text.x = element_blank(),
  axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
  
  YearsRepro_plot
    
    
    #Check model fit, residuals etc.
    
    autoplot(lm_YearsRepro)+
      theme_classic()
    
    shapiro.test(residuals(lm_YearsRepro))
    
  
```


## Yearly basking time

```{r}

#check data
gghistogram(res_ecto_stats$Bask_year, bins = 8)
ggboxplot(res_ecto_stats$Bask_year)


#Check lm model first
lm_BaskYear <- lm(Bask_year ~ Elevation + Species + Loc_type, data = res_ecto_stats)
lm_BaskYear_int <- lm(Bask_year ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_BaskYear_int2<- lm(Bask_year ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_BaskYear_int3<- lm(Bask_year ~ Elevation+Loc_type*Species, data = res_ecto_stats)

compare.fits(Bask_year ~Elevation | Species+Loc_type,
             data = res_ecto_stats, lm_BaskYear, lm_BaskYear_int)

compare.fits(Bask_year ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_BaskYear, lm_BaskYear_int2)

compare.fits(Bask_year ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_BaskYear, lm_BaskYear_int3)


AIC(lm_BaskYear, lm_BaskYear_int, lm_BaskYear_int2, lm_BaskYear_int3)
anova(lm_BaskYear, lm_BaskYear_int, lm_BaskYear_int2, lm_BaskYear_int3)

summary(lm_BaskYear) ## NO SIGNIFICANT INTERACTIONS
#summary(lm_BaskYear_int)
#summary(lm_BaskYear_int2)
#summary(lm_BaskYear_int3)


# Get summary and p values

    visualize(lm_BaskYear)
    
    Basking_plot <- visualize(lm_BaskYear, Bask_year~Elevation + Loc_type|Species, plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
      scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean yearly basking time (hours)")), x=NULL)+
          theme(strip.background = element_blank(),
  strip.text.x = element_blank(),
   axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
    
    Basking_plot
    
    #Check model fit, residuals etc.
    
    autoplot(lm_BaskYear)+
      theme_classic()
    
    shapiro.test(residuals(lm_BaskYear))
    
   #Check comparisons
            
    summary(glht(lm_BaskYear, linfct = mcp(Loc_type = 'Tukey')))
 

```

## Forage time



```{r}

#check data
gghistogram(res_ecto_stats$Forage_year, bins = 8)
ggboxplot(res_ecto_stats$Forage_year)


#Check lm model first

lm_ForageYear <- lm(Forage_year ~ Elevation + Species + Loc_type, data = res_ecto_stats)
lm_ForageYear_int <- lm(Forage_year ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_ForageYear_int2<- lm(Forage_year ~ Elevation*Loc_type+Species, data = res_ecto_stats)
lm_ForageYear_int3<- lm(Forage_year ~ Elevation+Loc_type*Species, data = res_ecto_stats)


compare.fits(Forage_year ~Elevation | Species+Loc_type,
             data = res_ecto_stats, lm_ForageYear, lm_ForageYear_int)

compare.fits(Forage_year ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_ForageYear, lm_ForageYear_int2)

compare.fits(Forage_year ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_ForageYear, lm_ForageYear_int3)


AIC(lm_ForageYear, lm_ForageYear_int, lm_ForageYear_int2, lm_ForageYear_int3)
anova(lm_ForageYear, lm_ForageYear_int, lm_ForageYear_int2, lm_ForageYear_int3)

summary(lm_ForageYear) ## NO SIGNIFICANT INTERACTION
#summary(lm_ForageYear_int)
#summary(lm_ForageYear_int2)
#summary(lm_ForageYear_int3)

    
# Plot
    
    visualize(lm_ForageYear)
   
    Forage_plot <-  visualize(lm_ForageYear, Forage_year~Elevation + Loc_type|Species, plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
                scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
      theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Mean yearly foraging time (hours)")), x="Elevation (m)")+
          theme(strip.background = element_blank(),
  strip.text.x = element_blank(),
   axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
    
    Forage_plot
    
    
    #Check model fit, residuals etc.
    
    autoplot(lm_ForageYear)+
      theme_classic()
    
    shapiro.test(residuals(lm_ForageYear))

    
   #Check comparisons
    
    summary(glht(lm_ForageYear, linfct = mcp(Loc_type = 'Tukey')))
 


```


## Fecundity per year

```{r}

#check data distribution
gghistogram(res_ecto_stats$Fecundity_year, bins = 15)
ggboxplot(res_ecto_stats$Fecundity_year)

#Check lm model first

lm_FecundityYear <- lm(Fecundity_year ~Elevation+ Species+Loc_type, data = res_ecto_stats)
lm_FecundityYear_int <- lm(Fecundity_year ~ Elevation*Species+Loc_type, data = res_ecto_stats)
lm_FecundityYear_int2<- lm(Fecundity_year ~Elevation*Loc_type+Species, data = res_ecto_stats)
lm_FecundityYear_int3<- lm(Fecundity_year ~Elevation+Loc_type*Species, data = res_ecto_stats)



compare.fits(Fecundity_year ~Elevation | Species+Loc_type,
             data = res_ecto_stats, lm_FecundityYear, lm_FecundityYear_int)

compare.fits(Fecundity_year ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_FecundityYear, lm_FecundityYear_int2)

compare.fits(Fecundity_year ~Elevation | Species+Loc_type, 
             data = res_ecto_stats, lm_FecundityYear, lm_FecundityYear_int3)


AIC(lm_FecundityYear, lm_FecundityYear_int, lm_FecundityYear_int2, lm_FecundityYear_int3)
anova(lm_FecundityYear, lm_FecundityYear_int, lm_FecundityYear_int2, lm_FecundityYear_int3)

#summary(lm_FecundityYear)
summary(lm_FecundityYear_int) ## significant interaction
#summary(lm_FecundityYear_int2)
#summary(lm_FecundityYear_int3)


    
  # Plot
    visualize(lm_FecundityYear_int)
    
  Fecundity_plot <-  visualize(lm_FecundityYear_int, Fecundity_year~Elevation + Loc_type|Species, plot="model")+
                scale_color_manual(values = c("firebrick", "gold", "navyblue"))+
                scale_shape_manual(values =c(19, 19, 19))+
                scale_linetype_manual(values =c(1, 1, 1))+
     theme_classic()+
      labs_pubr()+
      labs(title = NULL, y=expression(paste("Yearly fecundity (n. offspring)")), x="Elevation (m)")+
    theme(strip.background = element_blank(),
  strip.text.x = element_blank(),
  axis.text=element_text(size=11),
        axis.title=element_text(size=12,face="bold"))+
    facet_wrap(~Species)
  

  
  Fecundity_plot
  
    
    
#Check model fit, residuals etc.
    
    autoplot(lm_FecundityYear_int)+
      theme_classic()
    
    shapiro.test(residuals(lm_FecundityYear_int))
    
#Check comparisons
    summary(glht(lm_FecundityYear_int, linfct = mcp(Loc_type = 'Tukey')))
    
  
```




## Arrange plots

```{r}
plot_ecto <- ggarrange(EggDev_plot, Lifespan_plot, YearsRepro_plot, Basking_plot, Forage_plot, Fecundity_plot, nrow = 3, ncol = 2, labels = NULL, common.legend = FALSE, legend = "none", font.label = list(size = 13, color = "black", face = "bold"))

plot_ecto


ggsave("plot_ecto_final.pdf", plot=plot_ecto, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_final.svg", plot=plot_ecto, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300)
ggsave("plot_ecto_final.png", plot=plot_ecto, path = "../../Figures/Ectotherm_plots/", units="cm", width=20, height=20, dpi=300, bg="white")
```


